---
title: "Dataset Cleaning"
author: "John F. Brüne"
date: "2024-05-16"
output: html_document
---

# Data Cleaning Script

## Setup

### Load Packages

```{r setup, include = TRUE, results='hide', warning=FALSE}
knitr::opts_chunk$set(include = TRUE)

# Load the required libraries
library(dplyr)
library(caret)
library(tidyverse)
library(readxl)
library(lubridate)
library(stringr)
library(tictoc)
library(progress)
library(parallel)
library(foreach)
library(doParallel)
library(doSNOW)


```

### Load Functions

```{r}

# Function to be applied to each DataFrame
clean_and_format <- function(data) {
  # Date formatting
  data$Start <- as.Date(data$Start, format = "%Y-%m-%d")
  data$End <- as.Date(data$End, format = "%Y-%m-%d")
  data$Start <- format(data$Start, "%d %m %Y")
  data$End <- format(data$End, "%d %m %Y")

  # Convert 'Gender' to a factor
  data$Gender <- as.factor(data$Gender)

  # Rename columns for clarity
  data <- data %>%
    rename(birthdate = date, birthplace = place)

  # Remove unwanted columns
  data <- data %>%
    select(-sur, -family)

  # Reorder columns, optional depending on specific requirements
  data <- data %>%
    select(1:9, (ncol(.)-7):ncol(.), 10:(ncol(.)-8))

  return(data)
}

# Function to get the table based on the legislature
get_table <- function(legislature) {
  if (legislature == 6) {
    return(P6)
  } else if (legislature == 7) {
    return(P7)
  } else if (legislature == 8) {
    return(P8)
  } else if (legislature == 9) {
    return(P9)
  } else {
    stop("Invalid value in the Legislature column")
  }
}

# Function to add rapporteur nationality
add_raporteur_nat <- function(data) {
  num_cores <- parallel::detectCores() - 1
  cl <- makeCluster(num_cores)
  registerDoParallel(cl)
  
  tic("Block Execution Time")
  
  pb <- progress_bar$new(
    format = "  Processing [:bar] :percent :elapsed",
    total = nrow(data), 
    width = 60
  )
  
  results <- foreach(row = 1:nrow(data), .combine = rbind, .packages = c("dplyr"), .inorder = FALSE, .export = c("get_table", "P6", "P7", "P8", "P9")) %dopar% {
    pb$tick()
    
    Legislature <- data$Legislature[row]
    raporteur <- data$raporteur[row]
    
    table <- get_table(Legislature)
    
    rap_name_parts <- tolower(strsplit(as.character(raporteur), " ")[[1]])
    
    matches_lname <- which(sapply(table$Lname, function(x) {
      all(sapply(rap_name_parts, function(part) grepl(part, tolower(x))))
    }))
    
    if (length(matches_lname) == 0) {
      clean_full_name <- tolower(gsub(", ", " ", table$FullName))
      
      expected_full_name <- paste(rap_name_parts, collapse=" ")
      reversed_full_name <- paste(rev(rap_name_parts), collapse=" ")
      
      matches_fullname <- which(clean_full_name == expected_full_name | clean_full_name == reversed_full_name)
      
      if (length(matches_fullname) == 0) {
        combined_name <- tolower(paste(table$Fname, table$Lname, sep=" "))
        
        matches_combined <- which(combined_name == expected_full_name | combined_name == reversed_full_name)
        
        if (length(matches_combined) == 0) {
          NA
        } else {
          table$Country[matches_combined[1]]
        }
      } else {
        table$Country[matches_fullname[1]]
      }
    } else {
      table$Country[matches_lname[1]]
    }
  }
  
  data$raporteur_nat <- results
  
  toc()
  
  stopCluster(cl)
  
  return(data)
}

# Function to calculate loyalty score
calculate_loyalty_score <- function(politician_data, majority_votes_df) {
  loyalty_scores <- numeric(nrow(politician_data))
  
  for (index in 1:nrow(politician_data)) {
    epg <- as.character(politician_data$EPG[index])
    
    # Debugging: Output the current EPG value
    cat("EPG for Index", index, ":", epg, "\n")
    
    if (epg %in% rownames(majority_votes_df)) {
      epg_majority <- majority_votes_df[epg, ]
      matches <- 0
      total_votes <- 0
      for (i in 31:ncol(politician_data)) {  # Votes start at column 31
        vote_id <- names(politician_data)[i]
        if (!is.na(politician_data[[vote_id]][index]) && 
            politician_data[[vote_id]][index] != 0 &&  # Exclude persons with "0" in the row
            vote_id %in% names(epg_majority)) {
          matches <- matches + (politician_data[[vote_id]][index] == epg_majority[[vote_id]])
          total_votes <- total_votes + 1
        }
      }
      loyalty_scores[index] <- if (total_votes > 0) matches / total_votes else NA
      
      # Debugging: Output the matches and total votes for this index
      cat("Index:", index, "EPG:", epg, "Matches:", matches, "Total Votes:", total_votes, "Loyalty Score:", loyalty_scores[index], "\n")
    } else {
      loyalty_scores[index] <- NA
      
      # Debugging: Output if EPG is not found in majority_votes_df
      cat("EPG", epg, "not found in majority_votes_df for Index", index, "\n")
    }
  }
  
  politician_data$loyalty_score <- loyalty_scores
  return(politician_data)
}

# List of topic blocks and their associated topics
topic_blocks <- list(
  economic_votes = c("Economics", "Economic & monetary affairs", "Economic and monetary affairs"),
  social_votes = c("Employment & social affairs", "Employment & Social affairs"),
  foreign_policy_votes = c("Foreign & security policy", "Foreign& security policy", "Foreign and security policy"),
  industry_votes = c("Industry, research & energy", "Industry, Research & Energy"),
  health_votes = c("Environment & public health"),
  gender_votes = c("Gender equality"),
  law_votes = c("Judicial affairs", "Juridical Affairs", "Legal Affairs", "Legal affairs", "Constitutional and interconstitutional affairs", "International regulations of the EP", "Constitutional and inter-institutional affairs"),
  agriculture_fisheries_votes = c("Agriculture", "Fisheries"),
  budget_votes = c("Budget", "Budgetary Control"),
  civil_liberties_votes = c("Civil liberties, justice & home affairs"),
  education_votes = c("Culture & education"),
  petitions_votes = c("Petitions"),
  internal_market_votes = c("Internal market & consumer protection"),
  international_trade_votes = c("International trade"),
  regional_development_votes = c("Regional development", "Regioanal development", "Development"),
  transport_tourism_votes = c("Transport & tourism")
)

# Function to calculate the score for a topic block
calculate_block_score <- function(block_name, block_topics, votes_df, politician_data) {
  # Create an empty column for the score in the topic block in politician_data
  block_score_column <- paste0(block_name, "Score")
  politician_data[[block_score_column]] <- 0
  
  # Filter the votes for all topics in the topic block
  block_votes <- votes_df %>%
    filter(main_policy_name %in% block_topics)
  
  # Check if block_votes contains rows
  if (nrow(block_votes) > 0) {
    # Iterate through each row in the block_votes DataFrame
    for (i in 1:nrow(block_votes)) {
      # Get the Vote_ID for this row
      vote_id <- block_votes$Vote_ID[i]
      
      # Check if vote_id is not missing
      if (!is.na(vote_id)) {
        # Convert vote_id to string and check if it exists as a column in politician_data
        vote_id_str <- as.character(vote_id)
        if (vote_id_str %in% names(politician_data)) {
          # Increase or decrease the score based on the value in the column
          politician_data[[block_score_column]] <- politician_data[[block_score_column]] + ifelse(politician_data[[vote_id_str]] == 1, 1, ifelse(politician_data[[vote_id_str]] == 2, -1, 0))
        }
      }
    }
  } else {
    print(paste("No data found for topic block:", block_name))
  }
  
  # Return the updated politician_data
  return(politician_data)
}

# Function to calculate the activity index
calculate_activity_index <- function(data) {
  # Define weights for the different activities in the order of the columns
  weights <- c(3, 3, 3, 5, 4, 4, 3, 3, 2, 3, 3, 3, 4)
  
  # Define the columns with activity data in the dataset
  activity_columns <- 18:30
  
  # Calculate the mean for each row, considering NAs and weighting
  mean_values <- rowMeans(data[, activity_columns] * weights, na.rm = TRUE)
  
  # Apply Z-score normalization to the mean
  normalized_mean <- (mean_values - mean(mean_values, na.rm = TRUE)) / sd(mean_values, na.rm = TRUE)
  
  # Insert the activity index at the 32nd position
  data <- cbind(data[, 1:31], Activity_Index = normalized_mean, data[, 32:ncol(data)])
  
  return(data)
}

# Function to calculate age at start
calculate_age_at_start <- function(data) {
  # Convert birthdate and start date to the correct format
  data$birthdate <- as.Date(data$birthdate, format = "%Y-%m-%d")
  data$Start <- as.Date(data$Start, format = "%d %m %Y")
  
  # Calculate age at start
  data$age_at_start <- round(as.numeric(difftime(data$Start, data$birthdate, units = "days")/365), 1)
  
  # Move the new column to the 15th position in the dataset
  data <- cbind(data[, 1:14], Age_At_Start = data$age_at_start, data[, 15:ncol(data)])
  
  # Remove temporary columns
  data <- data %>%
    select(-c("age_at_start"))
  
  return(data)
}

# Function to calculate experience
calculate_experience <- function(data) {
  # Check if $first_start column contains missing values
  if (any(is.na(data$first_start))) {
    # Set experience to NA if first_start is NA
    data$experience <- NA
  } else {
    # Convert columns to the correct date format
    data$first_start <- as.Date(data$first_start, format = "%Y-%m-%dT%H:%M:%S")
    
    # Calculate the time difference between $first_start and $Start in days
    data$experience <- as.numeric(difftime(data$Start, data$first_start, units = "days"))
  }
  
  # Move the new column to the 16th position in the dataset
  data <- cbind(data[, 1:15], Experience = data$experience, data[, 16:ncol(data)])
  
  # Remove temporary columns
  data <- data[, !(names(data) %in% c("experience"))]
  
  return(data)
}

# Function to calculate the sum of terms
calculate_sum <- function(df, terms) {
  # Sum from Term1 to the desired Term (ignore NAs)
  sum <- rowSums(df[, terms], na.rm = TRUE)
  # If all terms are NAs, set experience at start to 0
  sum[is.na(sum)] <- 0
  return(sum)
}

# Function to calculate the winning score
calculate_winning_score <- function(politician_data, vote_results_df) {
  num_cores <- parallel::detectCores() - 1
  cl <- makeSOCKcluster(num_cores)
  registerDoSNOW(cl)
  
  legislature <- as.numeric(sub("P", "", deparse(substitute(politician_data))))
  legislature_votes <- vote_results_df[vote_results_df$Legislature == legislature, ]
  winning_scores <- numeric(nrow(politician_data))
  
  pb <- txtProgressBar(min = 0, max = nrow(politician_data), style = 3)
  
  start_time <- Sys.time()
  
  progress <- function(n) {
    elapsed <- Sys.time() - start_time
    setTxtProgressBar(pb, n)
    cat(sprintf("\rTime elapsed: %s", round(elapsed, 2)))
  }
  opts <- list(progress = progress)
  
  results <- foreach(index = 1:nrow(politician_data), .combine = rbind, .packages = c("dplyr"), .options.snow = opts) %dopar% {
    total_votes <- 0
    score <- 0
    
    for (i in 1:ncol(politician_data)) {
      vote_id <- names(politician_data)[i]
      
      if (vote_id %in% legislature_votes$Vote_ID) {
        politician_vote <- politician_data[index, vote_id]
        vote_result <- legislature_votes$result_code[legislature_votes$Vote_ID == vote_id]
        
        if (vote_result %in% c("+", "-", "-*")) {
          if (politician_vote != 0) {
            total_votes <- total_votes + 1
            
            if ((politician_vote == 1 && vote_result == "+") || 
                (politician_vote == 2 && vote_result == "-")) {
              score <- score + 1
            } else if ((politician_vote == 1 && vote_result == "-") || 
                       (politician_vote == 2 && vote_result == "+")) {
              score <- score - 1
            }
          }
        }
      }
    }
    
    winning_score <- if (total_votes > 0) score / total_votes else NA
    progress(index)
    
    return(winning_score)
  }
  
  close(pb)
  stopCluster(cl)
  
  politician_data$winning_score <- results
  return(politician_data)
}

# Function to calculate attendance score
calculate_attendance <- function(politician_data, vote_results_df) {
  num_cores <- parallel::detectCores() - 1
  cl <- makeSOCKcluster(num_cores)
  registerDoSNOW(cl)
  
  legislature <- as.numeric(sub("P", "", deparse(substitute(politician_data))))
  legislature_votes <- vote_results_df[vote_results_df$Legislature == legislature, ]
  
  valid_votes <- names(politician_data) %in% legislature_votes$Vote_ID
  
  pb <- txtProgressBar(min = 0, max = nrow(politician_data), style = 3)
  
  start_time <- Sys.time()
  
  progress <- function(n) {
    elapsed <- Sys.time() - start_time
    setTxtProgressBar(pb, n)
    cat(sprintf("\rTime elapsed: %s", round(elapsed, 2)))
  }
  opts <- list(progress = progress)
  
  results <- foreach(index = 1:nrow(politician_data), .combine = rbind, .packages = c("dplyr"), .options.snow = opts) %dopar% {
    votes <- as.numeric(politician_data[index, valid_votes])
    total_votes <- sum(!is.na(votes))
    attended_votes <- sum(votes != 0 & !is.na(votes))
    
    attendance_score <- if (total_votes > 0) attended_votes / total_votes else NA
    progress(index)
    
    return(attendance_score)
  }
  
  close(pb)
  stopCluster(cl)
  
  politician_data$attendance_score <- results
  return(politician_data)
}

```

## Data Import

#### Import and Format Politician Data

```{r}

EP6_RCVs_04_09 <- read_excel("EP6_RCVs_04_09.xlsx")
EP7_RCVs_09_14 <- read_excel("EP7_RCVs_09_14.xlsx")
EP8_RCVs_14_19 <- read_excel("EP8_RCVs_14_19.xlsx")
EP9_RCVs_19_22 <- read_excel("EP9_RCVs_19_22.xlsx")

ep_meps_info <- read_csv("ep_meps_info_final.csv")


```

```{r}

tic("Block Execution Time")

# Remove 'Activ' column if present
EP6_RCVs_04_09 <- EP6_RCVs_04_09 %>% select(-Activ)
EP8_RCVs_14_19 <- EP8_RCVs_14_19 %>% select(-Activ)
EP9_RCVs_19_22 <- EP9_RCVs_19_22 %>% select(-Activ)

# Rename 'MEP ID' column in EP7_RCVs_09_14 to 'WebisteEpID'
EP7_RCVs_09_14 <- EP7_RCVs_09_14 %>% rename(WebisteEpID = `MEP ID`)

# Create new 'full_name' column in EP7_RCVs_09_14 by combining 'Fname' and 'Lname'
EP7_RCVs_09_14$full_name <- paste(EP7_RCVs_09_14$Fname, EP7_RCVs_09_14$Lname, sep = " ")

# Merge datasets
P7 <- merge(EP7_RCVs_09_14, ep_meps_info, by.x = "full_name", by.y = "full", all.x = TRUE)

# Rename 'full_name' to 'full' in P7
P7 <- P7 %>% rename(full = full_name)

# Replace values in 'WebisteEpID' with values from 'UserID' and then delete 'UserID'
P7$WebisteEpID <- P7$UserID
P7 <- P7 %>% select(-UserID)

# Change the 'full' column to the tenth last one
P7 <- P7 %>%
  select(2:(ncol(P7)-9), 1, (ncol(P7)-8):ncol(P7))

# Merge datasets
P6 <- merge(EP6_RCVs_04_09, ep_meps_info, by.x = "WebisteEpID", by.y = "UserID", all.x = TRUE)
P8 <- merge(EP8_RCVs_14_19, ep_meps_info, by.x = "WebisteEpID", by.y = "UserID", all.x = TRUE)
P9 <- merge(EP9_RCVs_19_22, ep_meps_info, by.x = "WebisteEpID", by.y = "UserID", all.x = TRUE)

# Apply the function to the individual DataFrames
P6 <- clean_and_format(P6)
P7 <- clean_and_format(P7)
P8 <- clean_and_format(P8)
P9 <- clean_and_format(P9)

# Convert 'WebisteEpID' to integer
P6$WebisteEpID <- as.integer(P6$WebisteEpID)
P7$WebisteEpID <- as.integer(P7$WebisteEpID)
P8$WebisteEpID <- as.integer(P8$WebisteEpID)
P9$WebisteEpID <- as.integer(P9$WebisteEpID)

toc()


```

### Add Activity Data

```{r}

tic("Block Execution Time")

# Read data
activity_counts_term_term4 <- read_csv("activity_counts_term_term_4.csv")
activity_counts_term_term5 <- read_csv("activity_counts_term_term_5.csv")
activity_counts_term_term6 <- read_csv("activity_counts_term_term_6.csv")
activity_counts_term_term7 <- read_csv("activity_counts_term_term_7.csv")
activity_counts_term_term8 <- read_csv("activity_counts_term_term_8.csv")
activity_counts_term_term9 <- read_csv("activity_counts_term_term_9.csv")

# List of DataFrames
activity_counts_list <- list(activity_counts_term_term4, activity_counts_term_term5, activity_counts_term_term6,
                             activity_counts_term_term7, activity_counts_term_term8, activity_counts_term_term9)

# Convert 'mep_id' to character in all DataFrames
activity_counts_list <- lapply(activity_counts_list, function(df) {
  df$mep_id <- as.character(df$mep_id)
  return(df)
})

# Assign converted DataFrames back to original variables
names(activity_counts_list) <- c("activity_counts_term_term4", "activity_counts_term_term5", "activity_counts_term_term6",
                                 "activity_counts_term_term7", "activity_counts_term_term8", "activity_counts_term_term9")
list2env(activity_counts_list, envir = .GlobalEnv)

# Function to process terms
process_terms <- function(current_term, previous_terms) {
  # Ensure all DataFrames have the same column names and types
  columns_needed <- names(activity_counts_term_term6) # Based on Term 6
  current_term <- current_term[columns_needed]
  
  combined_data <- bind_rows(previous_terms, current_term)
  
  # Group and sum numeric values for each 'mep_id'
  combined_data %>%
    group_by(mep_id) %>%
    summarise(across(where(is.numeric), sum, na.rm = TRUE), .groups = "drop")
}

# Update Term 6
columns_needed <- names(activity_counts_term_term6)
activity_counts_term_term4 <- activity_counts_term_term4[columns_needed]
activity_counts_term_term5 <- activity_counts_term_term5[columns_needed]

# Convert relevant columns to character or numeric, especially 'mep_id'
activity_counts_term_term4$mep_id <- as.character(activity_counts_term_term4$mep_id)
activity_counts_term_term5$mep_id <- as.character(activity_counts_term_term5$mep_id)
activity_counts_term_term6$mep_id <- as.character(activity_counts_term_term6$mep_id)

# Merge DataFrames
combined_data <- bind_rows(activity_counts_term_term4, activity_counts_term_term5, activity_counts_term_term6)

# Group and sum numeric values for each 'mep_id'
updated_term6 <- combined_data %>%
  group_by(mep_id) %>%
  summarise(across(where(is.numeric), sum, na.rm = TRUE), .groups = "drop")

# Update Terms 7, 8, and 9
updated_term7 <- process_terms(activity_counts_term_term7, list(activity_counts_term_term4, activity_counts_term_term5, activity_counts_term_term6))
updated_term8 <- process_terms(activity_counts_term_term8, list(activity_counts_term_term4, activity_counts_term_term5, activity_counts_term_term6, updated_term7))
updated_term9 <- process_terms(activity_counts_term_term9, list(activity_counts_term_term4, activity_counts_term_term5, activity_counts_term_term6, updated_term7, updated_term8))

# Merge activity datasets
P6 <- merge(P6, updated_term6, by.x = "WebisteEpID", by.y = "mep_id", all.x = TRUE)
P7 <- merge(P7, updated_term7, by.x = "WebisteEpID", by.y = "mep_id", all.x = TRUE)
P8 <- merge(P8, updated_term8, by.x = "WebisteEpID", by.y = "mep_id", all.x = TRUE)
P9 <- merge(P9, updated_term9, by.x = "WebisteEpID", by.y = "mep_id", all.x = TRUE)

# Reorder columns
P6 <- P6 %>%
  select(1:17, (ncol(.)-12):ncol(.), 18:(ncol(.)-13))
P7 <- P7 %>%
  select(1:17, (ncol(.)-12):ncol(.), 18:(ncol(.)-13))
P8 <- P8 %>%
  select(1:17, (ncol(.)-12):ncol(.), 18:(ncol(.)-13))
P9 <- P9 %>%
  select(1:17, (ncol(.)-12):ncol(.), 18:(ncol(.)-13))

P8 <- P8 %>%
  select(1:8, 10:30, 9, everything())

# Create new column 'FullName' and fill with elements from 'full'
P8$FullName <- P8$full

# Move 'FullName' column to the fourth position
P8 <- P8 %>%
  select(1:3, FullName, everything())

toc()



```

### Check Colum Names

```{r}

# Extract the first 31 column names
names_P6 <- names(P6)[1:31]
names_P7 <- names(P7)[1:31]
names_P8 <- names(P8)[1:31]
names_P9 <- names(P9)[1:31]

# Check if the first 31 column names are the same
all_equal <- all(names_P6 == names_P7 & names_P6 == names_P8 & names_P6 == names_P9)

# Output the result
if (all_equal) {
  print("The first 31 column names are the same in all tables.")
} else {
  print("The first 31 column names are not the same in all tables.")
  
  # Optional: Display differences
  diff_P7 <- which(names_P6 != names_P7)
  diff_P8 <- which(names_P6 != names_P8)
  diff_P9 <- which(names_P6 != names_P9)
  
  print("Differences in P7:")
  print(diff_P7)
  
  print("Differences in P8:")
  print(diff_P8)
  
  print("Differences in P9:")
  print(diff_P9)
}

```

### Read Voting Data and Correct Date Formatting

```{r}

tic("Block Execution Time")

# Read voting data
EP6_9_Voted_docs <- read_excel("EP6_9_Voted docs.xlsx", 
                               col_types = c("numeric", "numeric", "text", 
                                             "numeric", "text", "text", "text", 
                                             "text", "text", "text", "text", "text", 
                                             "text", "text", "text", "text", "text", 
                                             "numeric", "text", "text", "text", 
                                             "text", "numeric", "numeric", "numeric", 
                                             "numeric", "numeric", "numeric"))

EP6_9_Voted_docs <- EP6_9_Voted_docs %>%
  mutate(date = as.character(date),
         date = case_when(
           # Convert Excel Serial Date (1900 system)
           grepl("^[0-9]+$", date) ~ as.Date(as.numeric(date), origin = "1899-12-30"),
           # Convert US format mm/dd/yyyy to EU format dd.mm.yyyy
           grepl("/", date) ~ as.Date(date, format = "%m/%d/%Y"),
           # EU format dd.mm.yyyy is already correct
           TRUE ~ as.Date(date, format = "%d.%m.%Y")
         ),
         # Format all valid dates in the desired format
         date = format(date, "%d.%m.%Y"))

toc()



```

### Add Raporateur Nationality

```{r}

tic("Block Execution Time")

# Apply the function to the DataFrame EP6_9_Voted_docs
EP6_9_Voted_docs <- add_raporteur_nat(EP6_9_Voted_docs)

EP6_9_Voted_docs <- EP6_9_Voted_docs %>%
  mutate(Rap_nat = as.character(raporteur_nat[,1])) %>%
  select(1:11, Rap_nat, everything(), -raporteur_nat)

toc()





```

# Calculation of Indices and Scores

### Loyalty Score

#### Debugging - Must be Executed

```{r}


# Function to rename EPG values and handle NAs
rename_and_handle_NAs <- function(data) {
  # Rename EPG values
  data <- data %>%
    mutate(EPG = case_when(
      EPG == "Greens/EFA" ~ "Greens_EFA",
      EPG == "S&D" ~ "Socialists_Democrats",
      TRUE ~ EPG
    ))
  
  # Replace NAs with "Non-attached Members"
  data$EPG[is.na(data$EPG)] <- "Non-attached Members"
  
  return(data)
}

P8 <- rename_and_handle_NAs(P8)
P9 <- rename_and_handle_NAs(P9)



```

#### Loyalty Scores Across All Four Legislatures

Duration: approx. 86 minutes

```{r}

tic("Block Execution Time")

# List of data
politician_data_list <- list(P6 = P6, P7 = P7, P8 = P8, P9 = P9)

# Main loop for P6, P7, P8, and P9
for (politician_data_name in names(politician_data_list)) {
  politician_data <- politician_data_list[[politician_data_name]]
  
  unique_epg <- unique(politician_data$EPG)
  unique_votes <- names(politician_data)[31:(ncol(politician_data))]
  
  majority_votes_list <- vector("list", length(unique_epg))
  
  for (i in seq_along(unique_epg)) {
    epg <- unique_epg[i]
    epg_data <- subset(politician_data, EPG == epg)
    epg_votes <- vector("numeric", length(unique_votes))
    
    for (j in seq_along(unique_votes)) {
      vote_id <- unique_votes[j]
      votes <- na.omit(epg_data[[vote_id]])
      votes <- votes[votes != 0]
      if (length(votes) > 0) {
        vote_mode <- as.numeric(names(which.max(table(votes))))
      } else {
        vote_mode <- NA
      }
      epg_votes[j] <- vote_mode
    }
    
    majority_votes_list[[i]] <- epg_votes
  }
  
  majority_votes_df <- do.call(rbind, majority_votes_list)
  colnames(majority_votes_df) <- unique_votes
  rownames(majority_votes_df) <- unique_epg
  majority_votes_df <- as.data.frame(majority_votes_df)
  
  # Debugging: Output the majority votes
  cat("Majority votes for", politician_data_name, ":\n")
  print(head(majority_votes_df))
  
  politician_data <- calculate_loyalty_score(politician_data, majority_votes_df)
  politician_data_list[[politician_data_name]] <- politician_data
  
  # Debugging: Check the calculated loyalty scores
  cat("Loyalty scores for", politician_data_name, ":\n")
  print(head(politician_data$loyalty_score))
}

toc()



```

```{r}
# Replace P6, P7, P8, and P9 with the updated data inside the list
P6 <- politician_data_list$P6
P7 <- politician_data_list$P7
P8 <- politician_data_list$P8
P9 <- politician_data_list$P9

# Move the 'loyalty_score' column to the 31st position
P6 <- P6 %>%
  select(1:30, loyalty_score = ncol(P6), everything())

P7 <- P7 %>%
  select(1:30, loyalty_score = ncol(P7), everything())

P8 <- P8 %>%
  select(1:30, loyalty_score = ncol(P8), everything())

P9 <- P9 %>%
  select(1:30, loyalty_score = ncol(P9), everything())


```


#### Visualize as 2x2 Plots

```{r}

# Set layout to a 2x2 grid
par(mfrow = c(2, 2))

# Create histograms
hist(P6$loyalty_score, main = "Loyalty Scores for P6", xlab = "Loyalty Score", ylab = "Number of MEPs", col = "lightblue", breaks = 30)
hist(P7$loyalty_score, main = "Loyalty Scores for P7", xlab = "Loyalty Score", ylab = "Number of MEPs", col = "lightblue", breaks = 30)
hist(P8$loyalty_score, main = "Loyalty Scores for P8", xlab = "Loyalty Score", ylab = "Number of MEPs", col = "lightblue", breaks = 30)
hist(P9$loyalty_score, main = "Loyalty Scores for P9", xlab = "Loyalty Score", ylab = "Number of MEPs", col = "lightblue", breaks = 30)


```


### Topic Scores

```{r}
tic("Block Execution Time")

votes_df <- EP6_9_Voted_docs

# List of data
politician_data_list <- list(P6 = P6, P7 = P7, P8 = P8, P9 = P9)

# Main loop for P6, P7, P8, and P9
for (politician_data_name in names(politician_data_list)) {
  politician_data <- politician_data_list[[politician_data_name]]
  legislature_number <- as.numeric(substr(politician_data_name, 2, 2)) # Extract the legislature
  
  # Filter votes for the current legislature and only final_vote == 1
  votes_df_filtered <- votes_df %>% 
    filter(Legislature == legislature_number & final_vote == 1)
  
  # Filter in politician_data only the votes that are present in votes_df_filtered
  politician_data <- politician_data %>% 
    select(1:31, intersect(names(politician_data), as.character(votes_df_filtered$Vote_ID)))
  
  # Ensure all columns except the first 31 are integers
  for (i in 32:ncol(politician_data)) {
    politician_data[[i]] <- as.integer(politician_data[[i]])
  }
  
  # Iterate through the topic blocks and calculate the score for each block
  for (block_name in names(topic_blocks)) {
    block_topics <- topic_blocks[[block_name]]
    politician_data <- calculate_block_score(block_name, block_topics, votes_df_filtered, politician_data)
  }
  
  # Select only the last 16 columns
  last_16_columns <- politician_data[, (ncol(politician_data) - 15):ncol(politician_data)]
  
  # Save the last 16 columns in the list
  politician_data_list[[politician_data_name]] <- last_16_columns
}

toc()



```

```{r}

# Access the original DataFrames and append the last 16 columns after column 31
P6 <- bind_cols(P6[, 1:31], politician_data_list$P6, P6[, 32:ncol(P6)])
P7 <- bind_cols(P7[, 1:31], politician_data_list$P7, P7[, 32:ncol(P7)])
P8 <- bind_cols(P8[, 1:31], politician_data_list$P8, P8[, 32:ncol(P8)])
P9 <- bind_cols(P9[, 1:31], politician_data_list$P9, P9[, 32:ncol(P9)])



```

### Activity Index

```{r}

# Column names for P6 18-30
colnames(P6)[18:30]

P6 <- calculate_activity_index(P6)
P7 <- calculate_activity_index(P7)
P8 <- calculate_activity_index(P8)
P9 <- calculate_activity_index(P9)


```


#### Visualize as 2x2 Plots
```{r}

# Set layout to a 2x2 grid
par(mfrow = c(2, 2))

# Create histograms
hist(P6$Activity_Index, main = "Activity Scores for P6", xlab = "Activity Score", ylab = "Number of MEPs", col = "lightblue", breaks = 50)
hist(P7$Activity_Index, main = "Activity Scores for P7", xlab = "Activity Score", ylab = "Number of MEPs", col = "lightblue", breaks = 50)
hist(P8$Activity_Index, main = "Activity Scores for P8", xlab = "Activity Score", ylab = "Number of MEPs", col = "lightblue", breaks = 50)
hist(P9$Activity_Index, main = "Activity Scores for P9", xlab = "Activity Score", ylab = "Number of MEPs", col = "lightblue", breaks = 50)


```


### Add CV and terms

```{r}

ep_meps_new <- read.csv("ep_meps_newCV.csv")

# Select the last four columns from ep_meps_new
ep_meps_new_selected <- ep_meps_new[, c("UserID", "terms", "first_start", "last_end", "first_cv")]

# Merge datasets P6, P7, P8, and P9 with the selected columns from ep_meps_new
P6 <- merge(P6, ep_meps_new_selected, by.x = "WebisteEpID", by.y = "UserID", all.x = TRUE)
P7 <- merge(P7, ep_meps_new_selected, by.x = "WebisteEpID", by.y = "UserID", all.x = TRUE)
P8 <- merge(P8, ep_meps_new_selected, by.x = "WebisteEpID", by.y = "UserID", all.x = TRUE)
P9 <- merge(P9, ep_meps_new_selected, by.x = "WebisteEpID", by.y = "UserID", all.x = TRUE)

# Move columns in P6
P6 <- P6 %>%
  select(1:16, (ncol(.) - 3):ncol(.), 17:(ncol(.) - 3))

# Repeat for P7, P8, P9
P7 <- P7 %>%
  select(1:16, (ncol(.) - 3):ncol(.), 17:(ncol(.) - 3))
P8 <- P8 %>%
  select(1:16, (ncol(.) - 3):ncol(.), 17:(ncol(.) - 3))
P9 <- P9 %>%
  select(1:16, (ncol(.) - 3):ncol(.), 17:(ncol(.) - 3))

# Replace 'CV' with 'first_cv' and then delete 'first_cv'
P6$CV <- P6$first_cv
P6 <- P6 %>%
  select(-first_cv)

P7$CV <- P7$first_cv
P7 <- P7 %>%
  select(-first_cv)

P8$CV <- P8$first_cv
P8 <- P8 %>%
  select(-first_cv)

P9$CV <- P9$first_cv
P9 <- P9 %>%
  select(-first_cv)



```


#### Manually Add Birthdates and Birthplaces

```{r}
P8$birthdate[P8$full == "Doru-Claudian FRUNZULICĂ"] <- as.Date("1959-07-08")
P8$birthplace[P8$full == "Doru-Claudian FRUNZULICĂ"] <- "Caracal"

P8$birthdate[P8$full == "Jacqueline FOSTER"] <- as.Date("1965-06-02")
P8$birthplace[P8$full == "Jacqueline FOSTER"] <- "Silchester"

P8$birthdate[P8$full == "Lucy ANDERSON"] <- as.Date("1973-02-13")
P8$birthplace[P8$full == "Lucy ANDERSON"] <- "Edinburgh"

P8$birthdate[P8$full == "Ian DUNCAN"] <- as.Date("1966-11-07")
P8$birthplace[P8$full == "Ian DUNCAN"] <- "Leeds"

P8$birthdate[P8$full == "John PROCTER"] <- as.Date("1947-12-30")
P8$birthplace[P8$full == "John PROCTER"] <- "Liverpool"

# For P9
P9$birthdate[P9$full == "Carles PUIGDEMONT I CASAMAJÓ"] <- as.Date("1962-12-29")
P9$birthplace[P9$full == "Carles PUIGDEMONT I CASAMAJÓ"] <- "Amer"

P9$birthdate[P9$full == "Dominik TARCZYŃSKI"] <- as.Date("1979-03-27")
P9$birthplace[P9$full == "Dominik TARCZYŃSKI"] <- "Lublin"

P9$birthdate[P9$full == "Manuela RIPA"] <- as.Date("1976-01-01")
P9$birthplace[P9$full == "Manuela RIPA"] <- "Saarbrücken"

P9$birthdate[P9$full == "Ernő SCHALLER-BAROSS"] <- as.Date("1987-01-30")
P9$birthplace[P9$full == "Ernő SCHALLER-BAROSS"] <- "Budapest"

P9$birthdate[P9$full == "Thijs REUTEN"] <- as.Date("1974-01-12")
P9$birthplace[P9$full == "Thijs REUTEN"] <- "Bussum"

P9$birthdate[P9$full == "Michiel HOOGEVEEN"] <- as.Date("1989-07-06")
P9$birthplace[P9$full == "Michiel HOOGEVEEN"] <- "Leiden"

P9$birthdate[P9$full == "Ilan DE BASSO"] <- as.Date("1969-10-01")
P9$birthplace[P9$full == "Ilan DE BASSO"] <- "Midyat"



```

#### Add Age and terms

```{r}

term_duration_dataframe <- read_csv("ep_meps_experience.csv")

# Loop to calculate age for each of the four tables
for (table_name in c("P6", "P7", "P8", "P9")) {
  assign(table_name, calculate_age_at_start(get(table_name)))
}

# For P6_1
P6_1 <- merge(P6, term_duration_dataframe, by.x = "WebisteEpID", by.y = "UserID", all.x = TRUE)
P6_1$Experience_at_Start <- calculate_sum(P6_1, c("Term_1", "Term_2", "Term_3", "Term_4", "Term_5")) 

# For P7_1
P7_1 <- merge(P7, term_duration_dataframe, by.x = "WebisteEpID", by.y = "UserID", all.x = TRUE)
P7_1$Experience_at_Start <- calculate_sum(P7_1, c("Term_1", "Term_2", "Term_3", "Term_4", "Term_5", "Term_6"))

# For P8_1
P8_1 <- merge(P8, term_duration_dataframe, by.x = "WebisteEpID", by.y = "UserID", all.x = TRUE)
P8_1$Experience_at_Start <- calculate_sum(P8_1, c("Term_1", "Term_2", "Term_3", "Term_4", "Term_5", "Term_6", "Term_7"))

# For P9_1
P9_1 <- merge(P9, term_duration_dataframe, by.x = "WebisteEpID", by.y = "UserID", all.x = TRUE)
P9_1$Experience_at_Start <- calculate_sum(P9_1, c("Term_1", "Term_2", "Term_3", "Term_4", "Term_5", "Term_6", "Term_7", "Term_8"))

P6 <- cbind(P6[,1:15], Experience_at_Start = P6_1$Experience_at_Start, P6[,16:ncol(P6)])
P7 <- cbind(P7[,1:15], Experience_at_Start = P7_1$Experience_at_Start, P7[,16:ncol(P7)])
P8 <- cbind(P8[,1:15], Experience_at_Start = P8_1$Experience_at_Start, P8[,16:ncol(P8)])
P9 <- cbind(P9[,1:15], Experience_at_Start = P9_1$Experience_at_Start, P9[,16:ncol(P9)])


```


##### Visualize as 2x2 Plots
```{r}
# Set layout to a 2x2 grid
par(mfrow = c(2, 2))

# Create histograms
hist(P6$Age_At_Start, main = "Age at Start for P6", xlab = "Age at Start", ylab = "Number of MEPs", col = "lightblue", breaks = 40)
hist(P7$Age_At_Start, main = "Age at Start for P7", xlab = "Age at Start", ylab = "Number of MEPs", col = "lightblue", breaks = 40)
hist(P8$Age_At_Start, main = "Age at Start for P8", xlab = "Age at Start", ylab = "Number of MEPs", col = "lightblue", breaks = 40)
hist(P9$Age_At_Start, main = "Age at Start for P9", xlab = "Age at Start", ylab = "Number of MEPs", col = "lightblue", breaks = 40)


```

```{r}
# Set layout to a 2x2 grid
par(mfrow = c(2, 2))

# Create histograms
hist(P6$Experience_at_Start, main = "Experience at Start for P6", xlab = "Experience at Start", ylab = "Number of MEPs", col = "lightblue", breaks = 10)
hist(P7$Experience_at_Start, main = "Experience at Start for P7", xlab = "Experience at Start", ylab = "Number of MEPs", col = "lightblue", breaks = 10)
hist(P8$Experience_at_Start, main = "Experience at Start for P8", xlab = "Experience at Start", ylab = "Number of MEPs", col = "lightblue", breaks = 10)
hist(P9$Experience_at_Start, main = "Experience at Start for P9", xlab = "Experience at Start", ylab = "Number of MEPs", col = "lightblue", breaks = 10)


```

## Writing final dataset

```{r}

# Save the DataFrames with age and term information
write_csv(P6, "P6_final.csv")
write_csv(P7, "P7_final.csv")
write_csv(P8, "P8_final.csv")
write_csv(P9, "P9_final.csv")

P6 <- read_csv("P6_final.csv")
P7 <- read_csv("P7_final.csv")
P8 <- read_csv("P8_final.csv")
P9 <- read_csv("P9_final.csv")


```
